\documentclass[UTF8]{ctexart}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{titlesec}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\large\bfseries}{\thesubsection}{1em}{}


\title{Xin-Qiang Cai}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Biography}
Currently, I am a second-year Ph.D. student of the \href{https://www.k.u-tokyo.ac.jp/complex/index_e.html}{Department of Complexity Science and Engineering} in \href{https://www.u-tokyo.ac.jp/en/}{The University of Tokyo} and a member of \href{http://www.ms.k.u-tokyo.ac.jp/}{Sugiyama-Yokoya-Ishida Lab}. Also, I am working as a research assistant on \href{https://beyondai.jp/}{Beyond AI Institution}.

I got my M.Sc. degree in \href{https://www.nju.edu.cn/en/7f/6b/c7136a163691/page.psp}{Computer Science and Technology} in June 2021 from \href{http://www.nju.edu.cn/}{Nanjing University} as a member of \href{http://www.lamda.nju.edu.cn/}{LAMDA} Group, supervised by professor \href{https://cs.nju.edu.cn/zhouzh/}{Zhi-Hua Zhou} and professor \href{http://www.lamda.nju.edu.cn/jiangy/}{Yuan Jiang}.

I got my B.Sc. degree in \href{http://hangkong.nwpu.edu.cn//}{Aircraft Design and Engineering} in June 2018 from \href{https://www.nwpu.edu.cn/}{Northwestern Polytechnical University}. In the same year, I was admitted to study for an M.Sc degree in \href{http://www.nju.edu.cn/}{Nanjing University} without an entrance examination.

\section*{Research Interests}
Currently, I am focusing on the subfields:
\begin{itemize}
    \item \textbf{Class Incremental Learning}: classification problems with emerging new classes;
    \item \textbf{Reinforcement Learning \& Imitation Learning}: learning a sequential-decision-making agent from the environment and/or demonstrations;
    \item \textbf{Learning with Weak Supervision}: learning a model from noisy, limited, or imprecise sources.
\end{itemize}

\section*{Preprint}
Kaiyan Zhao, Qiyu Wu, \textbf{Xin-Qiang Cai}, Yoshimasa Tsuruoka. \textit{Leveraging Multi-lingual Positive Instances in Contrastive Learning to Improve Sentence Embedding}. In: Arxiv. [\href{https://arxiv.org/abs/2309.08929}{arxiv}]

\section*{Publication}
% You can use \subsection*{} for each publication or \paragraph*{} or just write them in a list as below.
\begin{itemize}
    \item \textbf{Xin-Qiang Cai}, Yu-Jie\_Zhang, Chao-Kai Chiang, Masashi Sugiyama. \textit{Imitation Learning from Vague Feedback}. In: \textbf{Proceedings of the Thirty-seventh Conference on Neural Information Processing Systems (NeurIPS'23)}, New Orleans, US, Dec. 10-16, 2023. To Appear.
    \item \textbf{Xin-Qiang Cai}, Pushi Zhang, Li Zhao, Jiang Bian, Masashi Sugiyama, Ashley Juan Llorens. \textit{Distributional Pareto-Optimal Multi-Objective Reinforcement Learning}. In: \textbf{Proceedings of the Thirty-seventh Conference on Neural Information Processing Systems (NeurIPS'23)}, New Orleans, US, Dec. 10-16, 2023. To Appear.
    \item \textbf{Xin-Qiang Cai}, Yao-Xiang Ding, Zi-Xuan Chen, Yuan Jiang, Masashi Sugiyama, Zhi-Hua Zhou. \textit{Seeing Differently, Acting Similarly: Imitation Learning with Heterogeneous Observations}. In: \textbf{Proceedings of the Eleventh International Conference on Learning Representations (ICLR'23) (spotlight)}, Kigali, Rwanda, May 1-5, 2023.
    \item Zi-Xuan Chen*, \textbf{Xin-Qiang Cai*}, Yuan Jiang, Zhi-Hua Zhou. \textit{Anomaly Guided Policy Learning from Imperfect Demonstrations}. In: \textbf{Proceedings of the 21th International Conference on Autonomous Agents and Multi-Agent Systems (AAMAS'22) (oral)}, Auckland, New Zealand, May 9-13, 2022. Page: 244-252.
    \item \textbf{Xin-Qiang Cai}, Yao-Xiang Ding, Yuan Jiang, Zhi-Hua Zhou. \textit{Imitation Learning from Pixel-Level Demonstrations by HashReward}. In: \textbf{Proceedings of the 20th International Conference on Autonomous Agents and Multi-Agent Systems (AAMAS'21) (oral)}, online, May 3-7, 2021. Page: 279–287.
    \item \textbf{Xin-Qiang Cai}, Peng Zhao, Kai Ming Ting, Xin Mu, Yuan Jiang. \textit{Nearest Neighbor Ensembles: An Effective Method for Difficult Problems in Streaming Classification with Emerging New Classes}. In: \textbf{Proceedings of the 19th IEEE International Conference on Data Mining (ICDM'19)}, Beijing, China, Nov. 8-11, 2019. Page: 970-975.
    % Add other publications similarly.
\end{itemize}

\section*{Patent}
\begin{itemize}
    \item 一种摄像器材记录的视频图像数据的高维模仿学习方法. Patent No. 202011450396.1, 2020.
\end{itemize}

\section*{Service}
\subsection*{Conference}
\begin{itemize}
    \item NeurIPS 2023
    \item ICML 2023
    \item IJCAI 2023
    \item SDM 2023
    \item NeurIPS 2022
    \item UAI 2022
    \item ICML 2022
    \item IJCAI 2022
    \item CCML 2021
    \item IJCAI 2021
    \item ECAI 2020
    \item CIKM 2020
\end{itemize}
\subsection*{Journal}
\begin{itemize}
    \item \href{https://ieeexplore.ieee.org/xpl/RecentIssue.jsp?punumber=5962385}{IEEE Transactions on Neural Networks and Learning Systems(TNNLS)}
\end{itemize}

\section*{Awards \& Honors}
\begin{itemize}
    \item \href{https://www.jsps.go.jp/}{Japan Society for the Promotion of Science (JSPS, 日本学術振興会) DC2 Fellowship}. 2023
    \item MSRA Collaborative Research Program Fellowship (D-CORE 2022). 2022
    \item \href{https://spring-gx-appl.adm.s.u-tokyo.ac.jp/en/}{SPRING GX Fellowship}. 2021
    \item Excellent Graduate of Nanjing University. 2021
    \item AAMAS 2021 Attendance Scholarship. 2020
    \item Excellent Graduate Student of Nanjing University. 2019
    \item YeePay Scholarship of Nanjing University, Second Prize. 2019
    \item \href{http://icdm2019.bigke.org/}{ICDM Student Travel Award}. 2019
    \item \href{https://grawww.nju.edu.cn/9a/a6/c905a301734/page.psp}{Yingcai Scholarship of Nanjing University}, Second Prize. 2018
    \item Nanjing University Academic Scholarship, First Prize. 2018\&2019\&2020
    \item ZhongAn Hackathon Contest, AI scenario, First Prize. 2018
    \item Excellent Graduate of Northwestern Polytechnical University. 2018
    \item China Collegiate Computer Contest, First Prize. 2017
    \item The ACM-ICPC Asia Regional Contest, Qingdao Site 2017, Silver Medal. 2017
    \item The ACM-ICPC Asia Regional Contest, Xinjiang Site 2017, Bronze Medal. 2017
    \item Interdisciplinary Contest in Modeling, Honorable Mention. 2017
    \item China Collegiate Computer Contest, First Prize. 2017
    \item Interdisciplinary Contest in Modeling, Honorable Mention. 2016
    \item Contemporary Undergraduate Mathematical Contest in Modeling, Third Prize. 2016
    \item China Collegiate Programming Contest, Hangzhou Site 2016, Silver Medal. 2016
    \item China Collegiate Computer Contest, First Prize. 2016
    \item The ACM-ICPC Asia Regional Contest, Xi’an Site 2016, Bronze Medal. 2016
    \item The ACM-ICPC Asia Regional Contest, Shanghai Site 2016, Bronze Medal. 2016
    \item The ACM-ICPC Asia Regional Contest, China-Final, Bronze Medal. 2015
    \item Contemporary Undergraduate Mathematical Contest in Modeling, Second Prize. 2015
    \item The ACM-ICPC Asia Regional Contest, Shaanxi Provincial Contest, Silver Medal. 2015
    \item National Scholarship. 2015-2016
    \item National Scholarship. 2014-2015
    % Add other awards similarly.
\end{itemize}

\section*{Correspondence}
Email: cai@ms.k.u-tokyo.ac.jp, jkrsndivide@gmail.com

\end{document}
